---
title: "ISLR, chapter 2"
author: "ms"
date: "12/11/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, echo = FALSE, include=FALSE}
library(ISLR)
library(tidyverse)
here::here()
theme_set(theme_light())
```

### Figure 2.1
Description from ISLR:

>FIGURE 2.1. The `Advertising` data set. The plot displays `sales`, in thousands of units, as a function of `TV`, `radio`, and `newspaper` budgets, in thousands of dollars, for 200 diﬀerent markets. In each plot we show the simple least squares ﬁt of `sales` to that variable, as described in Chapter 3. In other words, each blue line represents a simple model that can be used to predict `sales` using `TV`, `radio`, and `newspaper`, respectively.

Getting this data was not straightforward. I located this data in an indirect reference in GitHub Inguen-toan's [repo](https://github.com/nguyen-toan/ISLR). Forked this repo for posterity, and will be using this instead

```{r}
Advertising <- read_csv('')
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
