---
title: "ISLR, chapter 1"
author: "ms"
date: "12/11/2019"
output: html_document
---


Require to load the ISLR package. Also, Tidyverse - my favorite swiss army knife
```{r echo=FALSE}
library(ISLR)
library(tidyverse)
here::here()
theme_set(theme_light())
```

### Figure 1.1

This requires us to load the `Wage` data. Let's load the data and look at it
```{r}
Wage = as_tibble(Wage)
Wage

```

Note that education has a lot of text which may not be useful for us. Let us convert that to a factor like follows:

```{r}
df <- Wage %>% 
  mutate(education = as.factor(as.numeric(substr(education, 1,1)))) 
  
```


Now the plot
```{r}
p1 <- df %>% 
  ggplot(aes(x = age, y = wage))+
  geom_point()+
  geom_smooth(se = FALSE)

p2 <- df %>% 
  ggplot(aes(x = year, y = wage))+
  geom_point()+
  stat_smooth(method = "lm", 
              formula = y ~ x)
p3 <- df %>% 
  ggplot(aes(x = education, y = wage, fill = education))+
  geom_boxplot()

ggpubr::ggarrange(p1, p2, p3, nrow = 1)
```

Save the plot

```{r}
ggsave(here::here("figures", "Chapter1","figure1_1.jpg"))
```

### Figure 1.2
This plot uses `Smarket` data. Loading...
```{r}
Smarket <- as_tibble(Smarket)
Smarket
```

Gather the dataset for facet-wrap. This is not probably what the authors did (_they may have done this using base-r, who knows?_) but this is the fastest and neatest.
```{r}
smarket <- Smarket %>% 
  select(Lag1, Lag2, Lag3, Direction) %>% 
  gather(key = "Lag", value = "Percentage change", c(1:3)) 
```
Now plot
```{r}
smarket %>% 
  ggplot(aes(x = Direction, y = `Percentage change`, fill = Direction))+
  geom_boxplot()+
  facet_wrap(~Lag, 
             strip.position = "top",
             labeller = as_labeller(c(Lag1 = "Yesterday", 
                                      Lag2 = "2 days previous",
                                      Lag3 = "3 days previous")))+
  ylab("Percentage change in S&P")+
  xlab("Today's Direction")

ggsave(here::here("figures","Chapter1","figure1_2.jpg"))
  
```

### Figure 1.3
We will come back to this after we cover quadratic discriminant analysis later

### Figure 1.4
We will come back to this after we cover principal component analysis later


